### 1.1

Create two objects in your environment, `x` and `y`. Assign `x` as a vector of numbers 1, 2, and 3. Assign `y` as a vector of numbers 4, 5, and 6. Once complete, check that both objects are visible in your RStudio environment.

```{r 1response}

x <- c (1, 2, 3)
y <- c (4, 5, 6)

### 1.2

Clear your environment. Check that `x` and `y` are no longer in the environment by typing each letter in the console. What is the result?

```{r 2response}
error result 
```

### 1.3

Check your R session info. Which version of R are you running? Which version of the `knitr` package are you running? Write these details below.

```{r 3response}
sessionInfo()
```

- R version: 4.5.0
- `knitr` version:1.50 


# Practice on Your Own!

### P.1

Create a vector `z` with the numbers 0 to 9. Set the seed for the R random number generator to 1234. Draw 5 numbers at random from `z` using the `sample()` function with `replace = TRUE`. Repeatedly run the code 3 times and note what you observe.

```{r P.1response}
z <- (0:9)
set.seed (1234)
sample (5, replace = TRUE)

numbers selected are the same each time 
```

### P.2

Run the `sample()` statement again, but this time without running the `set.seed()` line. What do you notice about the 5 numbers?

```{r P.2response}
sample (5, replace=TRUE)

numbers have now changed to different numbers
```
